Trends of SDR in Thessaloniki

### 2023-07-02 Article.Rmd
Commit 2023-07-02 14:17

@@

The SDR data used in this study cover the period from
January 1993 to March 2011, and were measured with
a Kipp & Zonen CM-21 pyranometer operating contin-
uously at the Laboratory of Atmospheric Physics of the
Aristotle University of Thessaloniki ($40^\deg$38"N, $22^\circ$57"E,
∼80 m above sea level). The monitoring site is located
near the city centre. The horizon is clear of obstruc-
◦ ◦
tions except for the azimuth angles between 35 and 120where obstacles of up to 10 elevation block the direct
irradiance in the morning for SZA larger than 80 .
These data points were excluded from the analysis, as

@@

<!-- time span -->
The SDR is equivalent to the whole sky Global radiation, also refered as Global Horizontal Irradiance (GHI), and was obtained with a horizontal leveled, CM-21 pyranometer.
SDR data spans the period of 
`r min(ALL_1_daily_DESEAS$Date)` to `r max(ALL_1_daily_DESEAS$Date)`.
In some algorithms we used as auxiliary data, the direct beam radiation (DNI) for comparisons, obtained by a CHP-1 pyrheliometer, with data availability from 
`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])` to `r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`.

@@

Using the mean daily SDR we produce the trends of each data set, as departure from the seasonal value.
Only for All-sky (Fig. \ref{fig:trendALL}) <!--and Cloudy-sky (Fig. \ref{fig:trendCLOUD})--> conditions, the statistical significance of the trends are acceptable (Tab. \ref{tab:trendtable}), to draw some conclusions.

>>>>

<!-- time span -->
The SDR is equivalent to the whole sky Global radiation (or Global Horizontal Irradiance, GHI), and was obtained with a horizontal leveled, CM-21 pyranometer, from \mbox{`r min(ALL_1_daily_DESEAS$Date)`} to \mbox{`r max(ALL_1_daily_DESEAS$Date)`}.
Also, we have measurements of direct beam radiation (DNI) obtained by a collocated CHP-1 pyrheliometer, from \mbox{`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`} to \mbox{`r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`}

In some algorithms, we used as auxiliary data, the direct beam radiation (DNI) for comparisons, obtained by a CHP-1 pyrheliometer, with data availability from  
`r min(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])` to `r max(ALL_1_daily_DESEAS[!is.na(DIR_att), Date])`.

@@

The SDR data used in this study cover the period from January 1993 to March 2011, and were measured with a Kipp & Zonen CM-21 pyranometer operating continuously at the Laboratory of Atmospheric Physics of the Aristotle University of Thessaloniki ( $40^\circ38'$N, $22^\circ57'$E, 80 m above sea level). The monitoring site is located
near the city centre. The horizon is clear of obstruc-
◦ ◦
tions except for the azimuth angles between 35 and 120where obstacles of up to 10 elevation block the direct
irradiance in the morning for SZA larger than 80 .
These data points were excluded from the analysis, as

@@

@@

Using the mean daily SDR we produce the trends of each data set, as departure from the seasonal value.
Only for All-sky (Fig.~\ref{fig:trendALL}) <!--and Cloudy-sky (Fig. \ref{fig:trendCLOUD})--> conditions, the statistical significance of the trends are acceptable (Tab.~\ref{tab:trendtable}), to draw some conclusions.
